MSDS6372Project1

### 2021-01-21 MSDS6372Project1.Rmd
adding program to convert Market.Category into column

**Data Import and Cleaning...**
```{r dataINC}
library(tidyverse)
# You need to adjust the work environment to run this code
setwd("/Users/mingyang/Desktop/SMU/Applied Statistics/MSDS6372Project1")
# Read in data under variable CarData
CarData = read.csv("data1.csv")
# In case there are NA character values
CarData[CarData=='NA'] <- NA
# Check the reading - can later be deleted
head(CarData)
str(CarData)
dim(CarData)
# Convert factor variables
variables.to.factor = c("Make","Model","Engine.Fuel.Type","Transmission.Type","Driven_Wheels","Market.Category","Vehicle.Size","Vehicle.Style")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
# Look at summary of data
summary(CarData)
summary(CarData$Engine.Fuel.Type)

missingData = CarData[rowSums(is.na(CarData)) > 0,]
missingData
dim(missingData)
```

>>>>

**Data Import and Cleaning...**
```{r dataINC}
library(tidyverse)
# You need to adjust the work environment to run this code
setwd("/Users/mingyang/Desktop/SMU/Applied Statistics/MSDS6372Project1")
# Read in data under variable CarData
CarData = read.csv("data1.csv")
# Fixing three empty values in CarData$Engine.Fuel.Type, after research they are regular unleaded
CarData$Engine.Fuel.Type = ifelse(CarData$Engine.Fuel.Type=="","regular unleaded",CarData$Engine.Fuel.Type)
# Fixing Engine Cylinders to 0 -- Mazda RX or Electrical Vehicle
CarData$Engine.Cylinders = ifelse(is.na(CarData$Engine.Cylinders),0,CarData$Engine.Cylinders)
# Fixing Tesla Model S with Number.of.Doors missing
CarData$Number.of.Doors = ifelse(CarData$Make=="Tesla"&is.na(CarData$Number.of.Doors),4,CarData$Number.of.Doors)
# Fixing Tesla HP with mean HP found online of 510
#CarData$Number.of.Doors = ifelse(CarData$Make=="Tesla"&is.na(CarData$Number.of.Doors),4,CarData$Number.of.Doors)
# Fixing Ferrari FF 2013 Number.of.Doors to 2 -- Google research
CarData$Number.of.Doors = ifelse(CarData$Make=="Ferrari"&is.na(CarData$Number.of.Doors),2,CarData$Number.of.Doors)

#Market.Category: Crossover,Diesel,Exotic,Luxury,High-Performance,Factory Tuner,Performance,Flex Fuel,Hatchback,Hybrid,N/A
marketCat = c("Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Performance","Flex Fuel","Hatchback","Hybrid","N/A")
marketCat = data.frame(marketCat)
str = "Hatchback,Factory Tuner,High-Performance,N/A";
grepl(marketCat[11,1],str)

# Add each Market Category as column
CarData['Crossover'] <- NA
CarData['Diesel'] <- NA
CarData['Exotic'] <- NA
CarData['Luxury'] <- NA
CarData['High-Performance'] <- NA
CarData['Factory Tuner'] <- NA
CarData['Performance'] <- NA
CarData['Flex Fuel'] <- NA
CarData['Hatchback'] <- NA
CarData['Hybrid'] <- NA
CarData['N/A'] <- NA

str(CarData)
# Use For loop to fill in Yes/No to each Market Category column
for(j in 1:dim(marketCat)[1]){
  CarData[marketCat[j,1]] = ifelse(grepl(marketCat[j,1],CarData$Market.Category),"Yes","No")
}

# Check the reading - can later be deleted
head(CarData)
str(CarData)
dim(CarData)
# Convert factor variables
variables.to.factor = c("Make","Model","Engine.Fuel.Type","Transmission.Type","Driven_Wheels","Market.Category","Vehicle.Size","Vehicle.Style","Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Performance","Flex Fuel","Hatchback","Hybrid","N/A")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
# Look at summary of data
summary(CarData)
summary(CarData$Market.Category)

missingData = CarData[rowSums(is.na(CarData)) > 0,]
missingData
dim(missingData)

#Looking at Tesla
#CarData %>% filter(Make=="Tesla")

# Looking at what to do with Market.Category variable
marketCat = CarData %>% select(MSRP,Market.Category)
dim(marketCat)
head(marketCat,100)

```
